### 2016-04-29 papers/thesis-vischer/Thesis.tex
add data for Brenden's thesis and make fac latex it

Figures ~\ref{F-T} through ~\ref{F-eta} show several computed thermodynamic quantities for the scrunched system. Each  It is worth noting that the two succeeding plots with respect to density have been interpolated; with a fixed cell size, it is only possible to simulate discrete filling fractions. The intervening points have been filled in using the Carnahan-Starling equation of state.  
\begin{figure}[H]
\centering
    \includegraphics[width=.75\textwidth]{Fexc-vs-T.pdf}
    \caption{Excess specific free energy as a function of temperature with each quantity scaled by well depth $\epsilon$. }
    \label{F-T}
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=.75\textwidth]{Shs-vs-eta.pdf}
    \caption{Hard sphere entropy as a function of density.}
    \label{Shs-eta}
\end{figure}
\ignore{Filling fraction or density? Value in distinction? We never use number density for the sake of units...}

\begin{figure}
    \centering
    \includegraphics[width=.75\textwidth]{Uexc-vs-eta.pdf}
    \caption{Preliminary results for free energy as a function of density. Solid line represents first doubling regime, [more]}
    \label{U-eta}
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=.75\textwidth]{Fexc-vs-eta.pdf}
    \caption{Preliminary results for free energy as a function of density. Solid line represents first doubling regime, [more]}
    \label{F-eta}
\end{figure}

>>>>

Figures ~\ref{F-T} through ~\ref{F-eta} show several computed thermodynamic quantities for the scrunched system. Each  It is worth noting that the two succeeding plots with respect to density have been interpolated; with a fixed cell size, it is only possible to simulate discrete filling fractions. The intervening points have been filled in using the Carnahan-Starling equation of state.  
\begin{figure}[H]
\centering
    \includegraphics[width=.75\textwidth]{../renormalization/figs/Fexc-vs-T.pdf}
    \caption{Excess specific free energy as a function of temperature with each quantity scaled by well depth $\epsilon$. }
    \label{F-T}
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=.75\textwidth]{../renormalization/figs/Shs-vs-eta.pdf}
    \caption{Hard sphere entropy as a function of density.}
    \label{Shs-eta}
\end{figure}
\ignore{Filling fraction or density? Value in distinction? We never use number density for the sake of units...}

\begin{figure}
    \centering
    \includegraphics[width=.75\textwidth]{../renormalization/figs/Uexc-vs-eta.pdf}
    \caption{Preliminary results for free energy as a function of density. Solid line represents first doubling regime, [more]}
    \label{U-eta}
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=.75\textwidth]{../renormalization/figs/Fexc-vs-eta.pdf}
    \caption{Preliminary results for free energy as a function of density. Solid line represents first doubling regime, [more]}
    \label{F-eta}
\end{figure}
